Rapid Epidemiological Analysis of Comorbidities and Treatments as risk factors for COVID-19 in Scotland (REACT-SCOT): a population-based case-control study

### 2020-06-19 casecontrol.Rmd
fixed miscoding of broad definition of fatal cases

# Tables
```{r demog, echo=FALSE, warning=FALSE, message=FALSE}
options(knitr.kable.NA = '')

knitr::kable(table.demog.append[, 1:5],
             escape=FALSE, 
             booktabs=TRUE,
             label="demog",
             row.names=FALSE,
             col.names=c("", clean.header(colnames(table.demog.aug)[1:2]),
                         "Rate ratio (95\\% CI)", "$p$-value"),
             align="lcccc", 
             caption="Univariate associations of severe disease with demographic factors") %>%
    column_spec(column=1, width="3cm") %>%
    column_spec(column=2, width="2cm") %>%
    column_spec(column=3, width="1.8cm") %>%
    column_spec(column=4, width="2.5cm") %>%
    kableExtra::group_rows("Ethnicity based on name classification", 1, 3, bold=FALSE) %>%
    kableExtra::group_rows("SIMD quintile", 4, 8, bold=FALSE) %>%
    kableExtra::group_rows("Ethnicity based on Scottish Morbidity Record", 10, 13, bold=FALSE,
               hline_before=TRUE, latex_gap_space="10pt") %>% 
    kable_styling(latex_options="hold_position")

>>>>

# Tables
```{r demog, echo=FALSE, warning=FALSE, message=FALSE}
options(knitr.kable.NA = '')
if(FALSE) {
knitr::kable(table.demog.append[, 1:5],
             escape=FALSE, 
             booktabs=TRUE,
             label="demog",
             row.names=FALSE,
             col.names=c("", clean.header(colnames(table.demog.aug)[1:2]),
                         "Rate ratio (95\\% CI)", "$p$-value"),
             align="lcccc", 
             caption="Univariate associations of severe disease with demographic factors") %>%
    column_spec(column=1, width="3cm") %>%
    column_spec(column=2, width="2cm") %>%
    column_spec(column=3, width="1.8cm") %>%
    column_spec(column=4, width="2.5cm") %>%
    kableExtra::group_rows("Ethnicity based on name classification", 1, 3, bold=FALSE) %>%
    kableExtra::group_rows("SIMD quintile", 4, 8, bold=FALSE) %>%
    kableExtra::group_rows("Ethnicity based on Scottish Morbidity Record", 10, 13, bold=FALSE,
               hline_before=TRUE, latex_gap_space="10pt") %>% 
    kable_styling(latex_options="hold_position") 
}
